\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\renewcommand{\labelitemi}{--}
\newenvironment{tightitemize}{
  \begin{itemize}
    \setlength{\itemsep}{1pt}
    \setlength{\topsep}{2pt}
    \setlength{\parsep}{0pt}
    \setlength{\partopsep}{0pt}
    \setlength{\parskip}{0pt}
  }{
  \end{itemize}
}

\newcommand{\resumeSubheading}[4]{
  \begin{tabularx}{\textwidth}{Xr}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabularx}
}

\newcommand{\resumeProject}[3]{
  \textbf{#1} \hfill \textit{#2}\\
  #3
}

\newcommand{\resumeSection}[1]{
  \vspace{4pt}
  {\large\bfseries #1}\\[-2pt]
  \hrule
  \vspace{1pt}
}

\begin{document}
\small

\begin{center}
    {\LARGE \textbf{Abhigyan Shekhar}}\\[4pt]
    \href{mailto:abhishanu07@gmail.com}{abhishanu07@gmail.com} \,|\, \href{https://www.linkedin.com/in/abhigyan-shekhar-4b3b8b344/}{LinkedIn} \,|\, \href{https://github.com/Abhigyan-Shekhar}{GitHub}
\end{center}

\resumeSection{Education}
\resumeSubheading
  {BMS College of Engineering}{Bengaluru, India}
  {Bachelor of Engineering in Computer Science}{Expected 2028}
\begin{tightitemize}
  \item CGPA: 8.3 (Third Sem)
  \item Relevant Coursework: Data Structures (C), OOP (Java), DBMS, Computer Organization, Calculus I--III
\end{tightitemize}

\resumeSection{Experience}
\resumeSubheading
  {Studyy}{Feb 2026 -- Present}
  {Intern}{Remote}
\begin{tightitemize}
  \item Built an LLM-based evaluation pipeline for OCR-extracted handwritten text that identifies question-answer pairs from inconsistent exam and note-style formatting.
  \item Developed backend onboarding flows with Google/Microsoft OAuth, email-password signup, email validation, and OTP-based forgot-password reset; designed prompt-driven answer scoring across relevance, completeness, correctness, clarity, and coherence.
\end{tightitemize}

\resumeSubheading
  {Cram \& Conquer}{Dec 2025 -- Present}
  {Frontend Developer Intern}{Remote}
\begin{tightitemize}
  \item Performed keyword research and built responsive landing pages in React/HTML/CSS to improve readability, SEO structure, and search visibility.
\end{tightitemize}

\resumeSection{Open Source Contributions}
\resumeProject
  {Kubernetes (Minikube)}{Go, Networking}
  {Merged PR \#22451: fixed \texttt{minikube mount} on macOS with the Podman driver by adding \texttt{host.containers.internal} support for routable host access.}

\resumeProject
  {Kubernetes (Core)}{Go, Concurrency}
  {Merged PR \#135759: fixed a race condition in the CEL admission policy compiler by analyzing concurrent map access and implementing thread-safe locking to prevent compiler panics during policy evaluation.}

\resumeProject
  {Kubernetes (Minikube)}{Go, System Architecture}
  {Merged PR \#22277: resolved a nested VM detection bug for macOS by updating the virtualization driver to correctly identify Apple Hypervisor capabilities.}

\resumeSection{Projects}
\resumeProject
  {BorderBridge \,|\, \href{https://github.com/Abhigyan-Shekhar/public-static-void-main}{GitHub}}{React, TypeScript, FastAPI, Supabase, XGBoost}
  {Built a refugee identity reconstruction and case-management platform with authority/refugee portals, explainable confidence scoring, evidence tracking, and referral workflows.}

\resumeProject
  {JeevBandhu \,|\, GitHub}{Python, AI Models, Prompt Engineering}
  {Integrated context-aware AI assistance into the platform using prompt engineering to improve response quality and relevance.}

\resumeProject
  {OCR QA Segmentation \,|\, GitHub}{Python, Machine Learning, OCR}
  {Built an OCR pipeline to segment document layouts and extract text for automated question answering.}

\resumeProject
  {Waggle MCP \,|\, GitHub}{Python, Graph Memory, Kubernetes}
  {Built a graph-based persistent memory system for AI agents using knowledge graph nodes/edges for decisions and contradictions; evaluated on ConvoMem, MemBench, and LongMemEval; added observability with Kubernetes deployment; achieved token-efficiency gains vs RAG (claimed \textasciitilde2--4x).}

\resumeSection{Achievements \& Research}
\begin{tightitemize}
  \item Winner, \textbf{Mega Hackathon} under the \textbf{Digital Border Management System} category, hosted by Protocol Club in collaboration with Team Codelocked, BMS College of Engineering (March 13--14, 2026).
  \item Currently working on a research paper comparing LLMs and RLMs across reasoning behavior, response quality, and system trade-offs.
  \item Active member of Team Code Locked and BMS MUNSOC, participating in competitive programming and Model UN conferences.
\end{tightitemize}

\resumeSection{Technical Skills}
\textbf{Languages:} Java (OOP), C, Python, JavaScript, TypeScript, SQL \\
\textbf{Frontend:} HTML, CSS, React.js, Tailwind CSS, Figma \\
\textbf{Backend/DB:} FastAPI, Supabase, MySQL, DBMS \\
\textbf{Cloud/Tools:} Kubernetes, Git, GitHub, Vercel, Render, Cursor, Claude \\
\textbf{Concepts:} SEO, Prompt Engineering, Machine Learning, Computer Architecture

\end{document}
